---
title: "Policy-Support and Air Quality"
author: "Vivien Henz"
description: "An Investigation on the Relationship between Voting Patterns Concerning Pro-Environmental Policies in U.S. Counties and Air Quality"
output:
  distill::distill_article:
    self_contained: false
---



## Introduction

```{r, echo=FALSE}
library(tidyverse)
```

```{r, echo=FALSE}
airquality <- read_csv("annual_aqi_by_county_2022.csv")
```

```{r, echo=FALSE}
climateviews <- read_csv("YCOM6.0_2021_Data_.csv")
```

#### Research Question
Does citizen-support for pro-environmental policies affect the air quality of U.S. counties?

I am interested in exploring data related to climate change and climate vulnerability. I think I could make an interesting project out of investigating whether or not the views of citizens on environmental policies actually have an impact on environmental improvements in their local area. This is worth exploring because it would give an insight into whether or not people's opinions actually matter when it comes to environmental efforts, and whether environmental improvements are driven by the will of the people, or more external factors.

#### Hypothesis
My hypothesis is that counties which host citizens which are more supportive towards pro-environmental policies will have better air quality.

I'm formulating this hypothesis on the assumption that people that tend to have more supportive views on environmental policies also tend to vote accordingly. This means that they will vote for candidates that, for example, will place greater emphasis on measures that reduce CO2 emissions within the county, such as public transport, industrial de-zoning, clean energy alternative projects and so on. I also base this hypothesis on my secondary assumption, which is that people that tend to have more supportive views on environmental policies also tend to choose to move to counties with better air quality; this is because air quality might become a push or pull factor for these more progressive people, meaning bad air quality in a county might drive people away while good air quality might attract people to move in to a county.

The explanatory variable that will be most important to my project will be the polling result of "Regulate CO2 as a pollutant: How much do you support or oppose the following policies?" from the Yale Climate Opinion Project, wherein habitants of a county responded to it, and the results were then aggregated as a percentage of county population that responded positively or negatively (Howe). 

My outcome variable will be county AQI scores. The Air Quality Index (AQI), is a scale of air pollutio, it tells "how clean or polluted the air is, and what associated health effects might be a concern, especially for ground-level ozone and particle pollution"(EPA). It is calculated by averaging out daily measurements made by air pollution monitors scattered around a county. The lower the AQI of a county is, the better its air quality.

An observed pattern where lower AQI scores are matched with more progressive views on environmental policies will proove my hypothesis. No pattern observed, or even an opposite pattern, where higher AQI scores correlate with more progressive views on environmental policies will disprove my hypothesis.







## Data 

```{r, echo=FALSE}

climateviews <- climateviews|>
  filter(GeoType == "County")

airquality <- airquality %>%
  unite("GeoName", County:State)
 
names(airquality)[4] <- 'good_days'
names(airquality)[16] <- 'pm25'
names(airquality)[12] <- 'median_aqi'
names(airquality)[11] <- 'aqi_90_percentile'

climateviews <- climateviews |> 
    mutate(gsub(" (County|Parish), ", "_", GeoName)) 

colnames(climateviews)[65] ="GeoName"
climateviews <- climateviews[, -3]

climateviews <- climateviews |>
  inner_join(airquality)
```

#### Data Source Description
In order to conduct my investigation, I merged two different datasets. The first, `airquality`, is a 2022 annual report on AQI in U.S. counties conducted by the EPA [Environmental Protection Agency], a U.S. government branch. The second, `climateviews`, is the results of a 2022 climate opinion poll conducted by the Yale Program on Climate Change Communication. It should be noted that this project is a cross-sectional study, due to the nature of the polling results used.

#### Independent Variable
This investigation's independent variable is issued from the `climateviews` dataset, and it is more precisely the result to the polling question that was sent out to habitants of every U.S. county: "Regulate CO2 as a pollutant: How much do you support or oppose the following policies?"(Howes). Respondents had the choice between four different answers, those being: Strongly support, Somewhat support, Somewhat oppose and Strongly oppose (Howes). The results were then classififed as percentages of respondents in each county that either showed support or opposed regulating CO2 as a pollutant.


#### Dependent Variable
This investigation's dependent variable is issued from the `airquality` dataset, and it is the 90th percentile of the averaged daily AQI scores of each U.S. county over the 2021 year. As mentioned in the hypothesis, the Air Quality Index is a scale of air pollution, it is measured by monitors scattered accross a county that track six different pollutents: CO2, SOx, Particulates, NO2 and O3 (EPA). The measurements are then aggregated, divided by a standard value, which is the value that the EPA deems as safe for the health of inhabitants in the measured area (EPA). The result is multiplied by 100 to give the final score. The AQI is divided into six categories: 0-50 is deemed good, 51-100 is moderate, 101-150 is unhealthy for sensitive groups, 151-200 is unhealthy, 201-300 is very unhealthy, 301-500 is hazardous (EPA).

The AQI scores for U.S. counties can summarized by the following distribution:

```{r, echo=FALSE}
climateviews |>
  ggplot(mapping = aes(x = aqi_90_percentile))+
  geom_histogram(fill = "dodgerblue1", color = "black")+
  theme_classic()+
  labs(title = "Dependent Variable Distribution", x = "County AQI score", y = "Frequency")

```
The majority of AQI scores in U.S. counties are located between the 40-80 range, crossing the good to moderate zones as classified by the EPA.




## Results

#### Primary Scatterplot

The main focus of this investigation falls in analysing the relationship between support for an pro-environmental policy in a county and the county's air quality. This can be visualized as follows:

```{r, echo=FALSE}
climateviews |>
  ggplot(mapping = aes(x = regulate,
                       y = aqi_90_percentile))+
  geom_point(alpha = 0.4, color = "dodgerblue1")+
  geom_smooth(method = "lm", se = T, color = "black")+
  theme_classic()+
  labs(title = "Support for Regulating CO2 as Pollutant and County AQI Score",
            x = "Percentage of County Pop. that Support Regulating CO2 as a Pollutant",
            y = "County AQI Score")
```

Drawing from the scatterplot's linear fit, there seems to be a weak positive correlation between support for regulating CO2 as a pollutant and county AQI scores. This, at first, seems to disprove my hypothesis, for this implies that the more people support a pro-environmental policy, the worse the air quality in their county gets. However, correlation does not mean causation, which leads us to make the following inferences. Firstly, there may be a confounding factor which influences the AQI scores of U.S. counties or/and the level of support for a pro-environmental policy. Secondly, the AQI score may actually be what influences people to support pro-environmental policies, because people exposed to high levels of air pollution in their county may be more sensitized to try to do something about it and therefore support those pro-environmental policies.

#### County Population as a Confounding Factor
Therefore, I identify county population as a confounding factor for both AQI scores and environmental policy support. I believe county population affects AQI scores because aggregating more people in an area tends to generate more pollution; due to these people using more cares, more electricity and so on. I also believe that county population affects support for regulating CO2 as a pollutant because of the relationship between political partisanship and urbanisation; bigger county populations often mean that the county is more urbanized, and, due to varying reasons, more liberal. More liberal populations tend to support environmental actions more than conservative populations. Therefore, counties with more people are more likely to support environmental action. Let us verify this with the following plots:

```{r,echo=FALSE}
plot1 <- climateviews|>
  ggplot(mapping = aes(x = log(TotalPop),
                       y = regulate))+
  geom_point(alpha = 0.4, color = "Dodgerblue1")+
  geom_smooth(method = "lm", se = T, color = "black")+
    theme_classic()+
  labs(title = "County Population and Support for Regulating CO2 as Pollutant",
       x = "Log of County Population",
       y = "Perc. of County Supporting Regulating CO2 as Pollutant")
plot1

plot2 <- climateviews|>
  ggplot(mapping = aes(x = log(TotalPop),
                       y = aqi_90_percentile))+
  geom_point(alpha = 0.4, color = "Dodgerblue1")+
  geom_smooth(method = "lm", se = T, color = "Black")+
    theme_classic()+
  labs(title = "County Population and AQI Score ",
       x = "Log of County Population",
       y = "AQI Score")
plot2

```
It is important to note that I take the log of county population and not population itself because county population in the U.S. varies from hundreds to millions, compressing the data and therefore producing ineffective visualizations. As we can see from the first scatterplot, there is a strong positive correlation between county population and support for regulating CO2 as a pollutant. In the second scatterplot, we can interpret that there is a somewhat weak positive correlation between county population and AQI scores. From these findings, we can confirm that population is an actual confounder in the inital relationship that we are investigating.


#### Multi-Variable Regression
Therefore, we can control for the confounder, that is the population variable, by utilizing a multi-variable regression, in which we plot support for regulating CO2 against AQI scores and the log of the population variable:

```{r, echo=FALSE}
library(infer)
reg_control <- lm(regulate ~ aqi_90_percentile + log(TotalPop), data = climateviews)


modelsummary::modelsummary(reg_control,title = "Table 1: CO2 Regulation Support, AQI Scores and Population Regression",
                           statistic = c("s.e. = {std.error}",
                                         "p = {p.value}"),
                           gof_map = c("nobs", "r.squared", "adj.r.squared"))

```
Here, the coefficient of -0.016 derived from `aqi_90_percentile` is of interest to this investigation. Causually speaking, this can be interpreted as the following: while controlling for county population, when support for regulating CO2 as a pollutant increases by 1%, the AQI score of the county decreases by 1.6%. I believe that this coefficient represents a causal effect. This supports my hypothesis that more favorable support for pro-environmental policies actually leads to better air quality in U.S. counties. However, we have to reject this result for the p-value is 0.148, meaning that the probability that this result is due to random chance is 14.8%, rendering it not statistically significant.

## Conclusion

To summarize this investigation, it was initially found that greater support for a pro-environmental policy actually decreased air quality in a county. However, the confounding factor of county population was identified, and I then integrated a multi-variable regression controlling for that confounding factor. Subsequently, it was found that for every increase in percentage point of support for regulating CO2 as a pollutant in a county, the air quality increased by 1.6% in the same county. However, this result had to be rejected due to it being non-statistically signficicant. I do not think that there is sufficient evidence to support my hypothesis. Firstly, my only supporting result is statistically non significant. Secondly, there may be more confounding variables that I have not been able to identify. Thirdly, and most importantly, my analysis is limited by the fact that there is still the possibility that poor air quality itself may drive people to support pro-environmental policies due to these people being more exposed and therefore more politically sensitized to the issue. My analysis could be improved by looking at the partisanship of different counties in order to assess its impact on air quality and more clearly identify the political slant of a the county. Furthermore, instead of focusing on counties, I could only focus on cities, comparing likewise areas with likewise areas and therefore eliminating much of the confounder.






## Works Cited
EPA. “Air Data Basic Information | US EPA.” EPA, 13 October 2022, https://www.epa.gov/outdoor-air-quality-data/air-data-basic-information. Accessed 14 December 2022.

Howe, P., Mildenberger, M., Marlon, J.R., and Leiserowitz, A., “Geographic variation in opinions on climate change at state and local scales in the USA,” Nature Climate Change. DOI: 10.1038/nclimate2583.
